---
title: "Overview of the prediction.game Package"
output: rmarkdown::html_vignette
author: "David Kane"
vignette: >
  %\VignetteIndexEntry{Overview of the prediction.game Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of this vignette is to provide an overview of the **prediction.game** package. I will also intersperse notes about future plans, for the reference of both potential collaborators and myself.

The only function is *play()* which allows for playing of the "prediction game," especially in class. Imagine that we are having a contest to determine who can come up with a number which is closest to a random draw from the *mpg* variable in the *mtcars* data frame. (There are `r length(mtcars$mpg)`  values for *mpg*, with a mean of `r round(mean(mtcars$mpg), 2)`.) 

```{r setup}
suppressMessages(library(tidyverse))
library(prediction.game)

play(n = 1000, guess_1 = 20.09, guess_2 = 19, formula = ~ sample(mtcars$mpg, size = 1)) %>% 
  count(winner)
```
